---
title: "Comparison of Peak Times Across Years in Fuji"
output: html_document
date: "2024-09-06"
---



#### Objective：
This analysis examines whether significant changes occurred in peak visitor times at various stations along the 吉田 Trail of Mount Fuji from July 2022 to 2024.

#### Research Thinking：
To evaluate whether there were significant changes in peak visitor times from July 2022 to 2024, the time with the highest daily visitor count was defined as the peak time of the day. Analyses were conducted separately for three stations along the 吉田 Trail of Mount Fuji: the trailhead, halfway station, and mountain station. Trends in peak visitor times for each station were plotted, and the Wilcoxon test was used to assess the significance of differences in peak times across the three years.

**Analysis using the Wilcoxon test:** The Wilcoxon test is a non-parametric test suitable for data that does not follow a normal distribution. Given the small sample size of peak time data and the non-normal distribution, the Wilcoxon test is more robust compared to other parametric tests. It also provides good statistical power for small sample sizes.

#### Research data：
Data bases: 2022/07, 2023/07, 2024/07

Selected **‘Trailhead location’**, **‘Half-way station’**, and **‘Mountain location’** of Mt. Fuji to check the number of people.
Data Collection Summary: The number of visitors was collected within a 0.5 km radius buffer of the study destination.

 - **Trailhead location**：富士スバルライン五合目-ビジターセンター
https://www.fujisan-climb.jp/trails/yoshida/index.html
 
 
 2022/7 = 2,482 people；2023/7 = 4,151 people；2024/7 = 1,759 people。


 - **Half-way station**：本八合目トモエ館
 
 
 2022/7 = 4,457 people；2023/7 = 4,287 people；2024/7 = 2,888 people。
 
 
 - **Mountain location**：富士山頂上 山口屋
 
 
 2022/7 = 6,475 people；2023/7 = 4,599 people；2024/7 = 3,825 people。



```{r setup, include=FALSE}
library(dplyr)
library(tidyr)
library(lubridate)
library(ggplot2)
library(ggsignif)
```


## 0 Extract daily peak hours
```{r, echo=FALSE}
path <- "/Users/liaojiajia/博士研究/NIES/富士/富士山山口/combine"
files <- list.files(path, pattern = "*.csv", full.names = TRUE)
all_data <- lapply(files, function(file) {
  read.csv(file, fileEncoding = "Shift-JIS", colClasses = c("Date" = "character"))
}) %>% bind_rows()
```

#### Raw data
```{r}
head(all_data)
```

```{r, echo=FALSE}
# 确保Date列转换为标准的日期格式
all_data$Date <- as.Date(all_data$Date, format = "%Y%m%d")

# 转换数据格式从宽格式到长格式，保留时间段名称
all_data_long <- all_data %>%
  mutate(pop = 男性 + 女性) %>% 
  select(Date, 富士山吉田登山口, pop) %>% 
  pivot_longer(
    cols = -c("富士山吉田登山口", "Date"), # 排除时间和日期列
    names_to = "Category",
    values_to = "Flow"
  )

# 转换时段为数值时间格式
all_data_long <- all_data_long %>%
  mutate(Time_Slot = gsub("時半", ":30", `富士山吉田登山口`),
         Time_Slot = gsub("時", ":00", Time_Slot),
         Time_Slot = format(strptime(Time_Slot, format = "%H:%M"), "%H:%M")) # 将时刻转换为标准时间格式

# 排除流量为0的时段，提取每个时段的最大人数
all_data_long <- all_data_long %>%
  filter(Flow > 0) %>%  # 排除流量为0的时段
  group_by(Date, `富士山吉田登山口`, Time_Slot) %>%
  summarise(Flow = max(Flow, na.rm = TRUE), .groups = "drop") 

# 确保每个日期的所有高峰时段被记录
daily_max_flow <- all_data_long %>%
  group_by(Date) %>%
  filter(Flow == max(Flow))  # 确保记录多个高峰点

# 添加年份列以便于后续分析
daily_max_flow$Year <- format(daily_max_flow$Date, "%Y")

# 定义一个函数用于绘制高峰时段分布图
plot_peak_visitor_times <- function(data, year) {
  # 转换为时间对象以确保时间顺序
  data$Time_Slot <- as.POSIXct(data$Time_Slot, format = "%H:%M")
  
  # 绘制指定年份7月份高峰时段的分布图
  ggplot(data, aes(x = Time_Slot)) +
    geom_bar(fill = "#e5ce81", color = "#e5ce81") +
    geom_text(stat = 'count', aes(label = ..count..), vjust = -0.3, position = position_dodge(width = 0.8)) +
    scale_x_datetime(date_labels = "%H:%M", date_breaks = "1 hour") + # X轴按照时间排序
    labs(title = paste("Peak Visitor Times in July at departure", year),
         x = "Time Slot",
         y = "Count of Peak Occurrences") +
    theme_minimal() +
    theme(axis.text.x = element_text(angle = 45, hjust = 1))
}
```

##### To extract the peak visitor times of the day, identify the time period with the highest number of visitors and generate the "daily_max_flow" dataset.

```{r}
 # Data samples
print(daily_max_flow)
```
**Time unit:** half an hour


**Flow：** number of people in the time period<br>


Explanation：In this example, between 16:30 and 19:00 on 2022/7/1, the number of visitors recorded every half hour was 33, which was the highest number recorded that day. Therefore, the peak period for that day is defined as these six time points from 16:30 to 19:00. For 2 July, 6時 was the highest and the peak point.

## 1 *Trailhead*_Yearly Analysis of Peak Visitor Hours 

### Trailhead location：富士スバルライン五合目-ビジターセンター
**（Analyse the frequency of occurrence of each peak hour）**

```{r, echo=FALSE}
# 修改绘图函数以适应多年的数据
plot_peak_visitor_times_multi_year <- function(data) {
  # 将时间转换为时间对象以确保时间顺序
  data$Time_Slot <- as.POSIXct(data$Time_Slot, format = "%H:%M")
  
  # 绘制多年的高峰时段分布图
  ggplot(data, aes(x = Time_Slot, fill = Year, color = Year)) +
    geom_bar(stat = 'count', position = 'dodge') +
    scale_x_datetime(date_labels = "%H:%M", date_breaks = "1 hour") + # X轴按照时间排序
    labs(title = "Peak Visitor Times in July at trailhead (2022-2024)",
         x = "Time Slot",
         y = "Count of Peak Occurrences") +
    theme_minimal() +
    theme(axis.text.x = element_text(angle = 45, hjust = 1))
}

# 提取2022-2024年7月份的数据并绘图
july_multi_year_data <- daily_max_flow %>%
  filter(month(Date) == 7)
plot_peak_visitor_times_multi_year(july_multi_year_data)

```


X-axis: indicates the different time periods of the day.


Y-axis: indicates the number of times these hours were selected as peak hours during the 31 days of July.

##### This chart shows the peak times at the trailhead point for the years 2022, 2023, and 2024.
 - **Overall, Peak hour at trailhead in 2024 became later in the day**
 - In 2022, the peak times were mainly between 1:00 PM and 4:00 PM.
 - In 2023, the peak times were similar to 2022, also concentrated between 1:00 PM and 4:00 PM, with no significant changes.
 - In 2024, the peak times were slightly delayed compared to the previous two years, concentrated between 2:00 PM and 5:00 PM.
 

### Wilcoxon test 
##### To test whether there are significant changes in peak times between the years, the Wilcoxon test was used for significance testing.

```{r, include=FALSE}
# 整理数据用于检验
# 统计每个 Time_Slot 在每个年份的总频次
peak_data <- daily_max_flow %>%
  group_by(Time_Slot, Year) %>%
  summarise(Frequency = n(), .groups = "drop")  # 正确统计每个时间段的频次

# 将频次数据转换为宽格式，以便于卡方检验等分析
peak_data_wide <- pivot_wider(peak_data, names_from = Year, values_from = Frequency, values_fill = list(Frequency = 0))
wilcox.test(peak_data_wide$`2023`, peak_data_wide$`2024`, paired = T)
wilcox.test(peak_data_wide$`2022`, peak_data_wide$`2024`, paired = T)
wilcox.test(peak_data_wide$`2022`, peak_data_wide$`2023`, paired = T)
```
```{r, echo=FALSE}
# 绘制每年高峰时刻的箱线图，并在各自的线上标记显著性
ggplot(daily_max_flow, aes(x = Year, y = as.numeric(format(as.POSIXct(Time_Slot, format = "%H:%M"), "%H")) + 
                             as.numeric(format(as.POSIXct(Time_Slot, format = "%H:%M"), "%M")) / 60)) +
  geom_boxplot(aes(fill = Year), show.legend = FALSE) +
  geom_jitter(width = 0.1, alpha = 0.5) +
  labs(title = "Significance of Changes in Peak Visitor Times by Year at Depature",
       x = "Year",
       y = "Peak Time (Hour of the Day)") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  # 添加显著性标记，并绘制为三条线
  geom_signif(
    comparisons = list(c("2022", "2023")),
    annotations = "NS.",
    map_signif_level = FALSE,
    y_position = 22 # 设置第一条线的位置
  ) +
  geom_signif(
    comparisons = list(c("2023", "2024")),
    annotations = "**",
    map_signif_level = FALSE,
    y_position = 23 # 设置第二条线的位置
  ) +
  geom_signif(
    comparisons = list(c("2022", "2024")),
    annotations = "***",
    map_signif_level = FALSE,
    y_position = 24 # 设置第三条线的位置
  )
```

##### significance testing：
 - There is no significant difference between 2022 and 2023.
 - There is a significant difference between 2022 and 2024, with the peak times in 2024 being later.
 - There is also a significant difference between 2023 and 2024, with a trend of delayed peak times.

## 2 Mountain_Yearly Analysis of Peak Visitor Hours  

### **Mountain location**：富士山頂上 山口屋

```{r, include=FALSE}
path <- "/Users/liaojiajia/博士研究/NIES/富士/富士登顶口/combine"

# 读取所有CSV文件，确保使用正确的编码
files <- list.files(path, pattern = "*.csv", full.names = TRUE)
all_data <- lapply(files, function(file) {
  read.csv(file, fileEncoding = "Shift-JIS", colClasses = c("Date" = "character"))
}) %>% bind_rows()

# 确保Date列转换为标准的日期格式
all_data$Date <- as.Date(all_data$Date, format = "%Y%m%d")

# 转换数据格式从宽格式到长格式，保留时间段名称
all_data_long <- all_data %>%
  mutate(pop = 男性 + 女性) %>% 
  select(Date, 富士山登口, pop) %>% 
  pivot_longer(
    cols = -c("富士山登口", "Date"), # 排除时间和日期列
    names_to = "Category",
    values_to = "Flow"
  )

# 转换时段为数值时间格式
all_data_long <- all_data_long %>%
  mutate(Time_Slot = gsub("時半", ":30", `富士山登口`),
         Time_Slot = gsub("時", ":00", Time_Slot),
         Time_Slot = format(strptime(Time_Slot, format = "%H:%M"), "%H:%M")) # 将时刻转换为标准时间格式

# 排除流量为0的时段，提取每个时段的最大人数
all_data_long <- all_data_long %>%
  filter(Flow > 0) %>%  # 排除流量为0的时段
  group_by(Date, `富士山登口`, Time_Slot) %>%
  summarise(Flow = max(Flow, na.rm = TRUE), .groups = "drop") 

# 确保每个日期的所有高峰时段被记录
daily_max_flow <- all_data_long %>%
  group_by(Date) %>%
  filter(Flow == max(Flow))  # 确保记录多个高峰点

# 添加年份列以便于后续分析
daily_max_flow$Year <- format(daily_max_flow$Date, "%Y")

# 定义一个函数用于绘制高峰时段分布图
plot_peak_visitor_times <- function(data, year) {
  # 转换为时间对象以确保时间顺序
  data$Time_Slot <- as.POSIXct(data$Time_Slot, format = "%H:%M")
  
  # 绘制指定年份7月份高峰时段的分布图
  ggplot(data, aes(x = Time_Slot)) +
    geom_bar(fill = "#e5ce81", color = "#e5ce81") +
    geom_text(stat = 'count', aes(label = ..count..), vjust = -0.3, position = position_dodge(width = 0.8)) +
    scale_x_datetime(date_labels = "%H:%M", date_breaks = "1 hour") + # X轴按照时间排序
    labs(title = paste("Peak Visitor Times in July at Summit", year),
         x = "Time Slot",
         y = "Count of Peak Occurrences") +
    theme_minimal() +
    theme(axis.text.x = element_text(angle = 45, hjust = 1))
}
```


```{r, echo=FALSE}
# 修改绘图函数以适应多年的数据
plot_peak_visitor_times_multi_year <- function(data) {
  # 将时间转换为时间对象以确保时间顺序
  data$Time_Slot <- as.POSIXct(data$Time_Slot, format = "%H:%M")
  
  # 绘制多年的高峰时段分布图
  ggplot(data, aes(x = Time_Slot, fill = Year, color = Year)) +
    geom_bar(stat = 'count', position = 'dodge') +
    scale_x_datetime(date_labels = "%H:%M", date_breaks = "1 hour") + # X轴按照时间排序
    labs(title = "Peak Visitor Times in July at Mountain (2022-2024)",
         x = "Time Slot",
         y = "Count of Peak Occurrences") +
    theme_minimal() +
    theme(axis.text.x = element_text(angle = 45, hjust = 1))
}

# 提取2022-2024年7月份的数据并绘图
july_multi_year_data <- daily_max_flow %>%
  filter(month(Date) == 7)
plot_peak_visitor_times_multi_year(july_multi_year_data)

```


X-axis: indicates the different time periods of the day.


Y-axis: indicates the number of times these hours were selected as peak hours during the 31 days of July.

##### This chart shows the peak times at the mountain for the years 2022, 2023, and 2024.
 - Overall, **Peak hour at mountain in 2024 became later in the day**, compared to the previous two years.
 - In 2022, the peak times were mainly between 8:00 AM and 12:00 PM, with some extending to around 3:00 PM.
 - In 2023, the peak times were delayed compared to 2022, mainly between 10:00 AM and 2:00 PM.
 - In 2024, the peak times were further delayed compared to 2022 and 2023, concentrated between 1:00 PM and 5:00 PM.

```{r, include=FALSE}
peak_data <- daily_max_flow %>%
  group_by(Time_Slot, Year) %>%
  summarise(Frequency = n(), .groups = "drop")  # 正确统计每个时间段的频次

# 将频次数据转换为宽格式，以便于卡方检验等分析
peak_data_wide <- pivot_wider(peak_data, names_from = Year, values_from = Frequency, values_fill = list(Frequency = 0))
wilcox.test(peak_data_wide$`2023`, peak_data_wide$`2024`, paired = T)
wilcox.test(peak_data_wide$`2022`, peak_data_wide$`2024`, paired = T)
wilcox.test(peak_data_wide$`2022`, peak_data_wide$`2023`, paired = T)
```


### Wilcoxon test 

```{r, echo=FALSE}
ggplot(daily_max_flow, aes(x = Year, y = as.numeric(format(as.POSIXct(Time_Slot, format = "%H:%M"), "%H")) + 
                             as.numeric(format(as.POSIXct(Time_Slot, format = "%H:%M"), "%M")) / 60)) +
  geom_boxplot(aes(fill = Year), show.legend = FALSE) +
  geom_jitter(width = 0.1, alpha = 0.5) +
  labs(title = "Significance of Changes in Peak Visitor Times by Year at Mountain",
       x = "Year",
       y = "Peak Time (Hour of the Day)") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  # 添加显著性标记，并绘制为三条线
  geom_signif(
    comparisons = list(c("2022", "2023")),
    annotations = "NS.",
    map_signif_level = FALSE,
    y_position = 22 # 设置第一条线的位置
  ) +
  geom_signif(
    comparisons = list(c("2023", "2024")),
    annotations = "**",
    map_signif_level = FALSE,
    y_position = 23 # 设置第二条线的位置
  ) +
  geom_signif(
    comparisons = list(c("2022", "2024")),
    annotations = "***",
    map_signif_level = FALSE,
    y_position = 24 # 设置第三条线的位置
  )

```



##### significance testing：
 - There is no significant difference between 2022 and 2023; the peak times in these two years are quite close.
 - There is a highly significant difference between 2022 and 2024, indicating a significant delay in peak times.
 - There is a significant difference between 2023 and 2024, with a clear trend of delayed peak times.


## 3 Half_Yearly Analysis of Peak Visitor Hours 

### **Half-way station**：本八合目トモエ館

```{r, include=FALSE}
path <- "/Users/liaojiajia/博士研究/NIES/富士/半山腰休息站/combine"

# 读取所有CSV文件，确保使用正确的编码
files <- list.files(path, pattern = "*.csv", full.names = TRUE)
all_data <- lapply(files, function(file) {
  read.csv(file, fileEncoding = "Shift-JIS", colClasses = c("Date" = "character"))
}) %>% bind_rows()

# 确保Date列转换为标准的日期格式
all_data$Date <- as.Date(all_data$Date, format = "%Y%m%d")

# 转换数据格式从宽格式到长格式，保留时间段名称
all_data_long <- all_data %>%
  mutate(pop = 男性 + 女性) %>% 
  select(Date, 本八合目.中途登山口., pop) %>% 
  pivot_longer(
    cols = -c("本八合目.中途登山口.", "Date"), # 排除时间和日期列
    names_to = "Category",
    values_to = "Flow"
  )

# 转换时段为数值时间格式
all_data_long <- all_data_long %>%
  mutate(Time_Slot = gsub("時半", ":30", `本八合目.中途登山口.`),
         Time_Slot = gsub("時", ":00", Time_Slot),
         Time_Slot = format(strptime(Time_Slot, format = "%H:%M"), "%H:%M")) # 将时刻转换为标准时间格式

# 排除流量为0的时段，提取每个时段的最大人数
all_data_long <- all_data_long %>%
  filter(Flow > 0) %>%  # 排除流量为0的时段
  group_by(Date, `本八合目.中途登山口.`, Time_Slot) %>%
  summarise(Flow = max(Flow, na.rm = TRUE), .groups = "drop") 

# 确保每个日期的所有高峰时段被记录
daily_max_flow <- all_data_long %>%
  group_by(Date) %>%
  filter(Flow == max(Flow))  # 确保记录多个高峰点

# 添加年份列以便于后续分析
daily_max_flow$Year <- format(daily_max_flow$Date, "%Y")

# 定义一个函数用于绘制高峰时段分布图
plot_peak_visitor_times <- function(data, year) {
  # 转换为时间对象以确保时间顺序
  data$Time_Slot <- as.POSIXct(data$Time_Slot, format = "%H:%M")
  
 print(daily_max_flow)
  
   # 绘制指定年份7月份高峰时段的分布图
  ggplot(data, aes(x = Time_Slot)) +
    geom_bar(fill = "#e5ce81", color = "#e5ce81") +
    geom_text(stat = 'count', aes(label = ..count..), vjust = -0.3, position = position_dodge(width = 0.8)) +
    scale_x_datetime(date_labels = "%H:%M", date_breaks = "1 hour") + # X轴按照时间排序
    labs(title = paste("Peak Visitor Times in July at Summit at Half", year),
         x = "Time Slot",
         y = "Count of Peak Occurrences") +
    theme_minimal() +
    theme(axis.text.x = element_text(angle = 45, hjust = 1))
}
```


```{r, echo=FALSE}
# 修改绘图函数以适应多年的数据
plot_peak_visitor_times_multi_year <- function(data) {
  # 将时间转换为时间对象以确保时间顺序
  data$Time_Slot <- as.POSIXct(data$Time_Slot, format = "%H:%M")
  
  # 绘制多年的高峰时段分布图
  ggplot(data, aes(x = Time_Slot, fill = Year, color = Year)) +
    geom_bar(stat = 'count', position = 'dodge') +
    scale_x_datetime(date_labels = "%H:%M", date_breaks = "1 hour") + # X轴按照时间排序
    labs(title = "Peak Visitor Times in July at Half (2022-2024)",
         x = "Time Slot",
         y = "Count of Peak Occurrences") +
    theme_minimal() +
    theme(axis.text.x = element_text(angle = 45, hjust = 1))
}

# 提取2022-2024年7月份的数据并绘图
july_multi_year_data <- daily_max_flow %>%
  filter(month(Date) == 7)
plot_peak_visitor_times_multi_year(july_multi_year_data)

```



X-axis: indicates the different time periods of the day.


Y-axis: indicates the number of times these hours were selected as peak hours during the 31 days of July.

##### Content: This chart illustrates the peak times at the Half for the years 2022, 2023, and 2024.
 - **Overall, Peak hour at Half in 2024 became earlier in the day**, compared to the previous two years.
 - In 2022, the peak times were mainly concentrated between 10:00 AM and 8:00 PM.
 - In 2023, the peak times were similar to 2022 but slightly delayed, mainly occurring between 11:00 AM and 9:00 PM.
 - In 2024, the peak times were noticeably earlier, concentrated between 6:00 AM and 10:00 AM.

### Wilcoxon test 

```{r, include=FALSE}
peak_data <- daily_max_flow %>%
  group_by(Time_Slot, Year) %>%
  summarise(Frequency = n(), .groups = "drop")  # 正确统计每个时间段的频次

# 将频次数据转换为宽格式，以便于卡方检验等分析
peak_data_wide <- pivot_wider(peak_data, names_from = Year, values_from = Frequency, values_fill = list(Frequency = 0))
wilcox.test(peak_data_wide$`2023`, peak_data_wide$`2024`, paired = T)
wilcox.test(peak_data_wide$`2022`, peak_data_wide$`2024`, paired = T)
wilcox.test(peak_data_wide$`2022`, peak_data_wide$`2023`, paired = T)
```
```{r, echo=FALSE}
ggplot(daily_max_flow, aes(x = Year, y = as.numeric(format(as.POSIXct(Time_Slot, format = "%H:%M"), "%H")) + 
                             as.numeric(format(as.POSIXct(Time_Slot, format = "%H:%M"), "%M")) / 60)) +
  geom_boxplot(aes(fill = Year), show.legend = FALSE) +
  geom_jitter(width = 0.1, alpha = 0.5) +
  labs(title = "Significance of Changes in Peak Visitor Times by Year at Half",
       x = "Year",
       y = "Peak Time (Hour of the Day)") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  # 添加显著性标记，并绘制为三条线
  geom_signif(
    comparisons = list(c("2022", "2023")),
    annotations = "NS.",
    map_signif_level = FALSE,
    y_position = 22 # 设置第一条线的位置
  ) +
  geom_signif(
    comparisons = list(c("2023", "2024")),
    annotations = "**",
    map_signif_level = FALSE,
    y_position = 23 # 设置第二条线的位置
  ) +
  geom_signif(
    comparisons = list(c("2022", "2024")),
    annotations = "***",
    map_signif_level = FALSE,
    y_position = 24 # 设置第三条线的位置
  )

```


##### significance testing：
 - There is no significant difference between 2022 and 2023; the peak times in these two years are quite similar.
 - There is a significant difference between 2022 and 2024, with a noticeable shift to earlier peak times in 2024.
 - There is a significant difference between 2023 and 2024, further indicating an earlier occurrence of peak times in 2024.

## 4 Data feasibility testing

To verify the reliability of the data：I compared the visitor data from the Trailhead with the daily visitor data recorded by MOE for the "吉田ルート" in July 2023 to verify the reliability of the analysis. Please note that the MOE data represents the total number of visitors per day and does not include the number of visitors at each time point.


MOE：https://kanto.env.go.jp/press_00050.html



##### Merging of the two data


 - Daily_Total_Visitors：Number of daily visitors in Trailhead


 - yoshida：：Number of daily visitors in WOE “吉田ルート”
```{r, echo=FALSE}
# Step 1: 读取官方数据和用户数据
official_data <- read.csv("/Users/liaojiajia/Downloads/moe_count.csv")  # 请替换为官方数据文件的路径
user_data <- read.csv("/Users/liaojiajia/博士研究/NIES/富士/求和/daily_totals_july_2023.csv")  # 使用您计算好的每日总游客数文件

# Step 2: 转换日期为标准格式
official_data$date <- as.Date(official_data$date, format = "%Y-%m-%d")  # 假设官方数据日期格式为 "YYYY-MM-DD"
user_data$Date <- as.Date(user_data$Date)  # 确保用户数据中的日期格式正确

# Step 3: 筛选 2023 年 7 月的数据
official_july_2023 <- official_data %>%
  filter(year(date) == 2023 & month(date) == 7)

user_july_2023 <- user_data %>%
  filter(year(Date) == 2023 & month(Date) == 7)

#合并数据集，按日期匹配
merged_data <- merge(user_july_2023, official_july_2023, by.x = "Date", by.y = "date")
print(head(merged_data))
```

##### Normality test
```{r, echo=FALSE}
shapiro.test(merged_data$Daily_Total_Visitors)
shapiro.test(merged_data$yoshida)
plot(merged_data$Daily_Total_Visitors, merged_data$yoshida, main="Scatter Plot", xlab="Your Data", ylab="Official Data")
```



 According to the results of the Shapiro-Wilk normality test, neither dataset follows a normal distribution, making the Spearman correlation test a more appropriate choice.
 - For the KDDI dataset, the p-value is much less than 0.05, indicating that the data does not follow a normal distribution. 
 - For the MOE dataset, the p-value is also less than 0.05, showing that this data does not follow a normal distribution either.


##### Spearman correlation test
```{r, echo=FALSE}
# 计算 Spearman 相关系数
correlation_spearman <- cor(merged_data$Daily_Total_Visitors, merged_data$yoshida, method = "spearman", use = "complete.obs")
# 输出 Spearman 相关系数结果
print(paste("The Spearman correlation between Daily_Total_Visitors and Yoshida for July 2023 is:", correlation_spearman))
ggplot(merged_data, aes(x = Daily_Total_Visitors, y = yoshida)) +
  geom_point(color = "blue", alpha = 0.6) +  # 绘制散点图
  geom_smooth(method = "lm", color = "red", se = FALSE) +  # 添加线性回归线
  labs(
    title = "Scatter Plot of Daily Total Visitors vs Yoshida (July 2023)",
    x = "Your Data: Daily Total Visitors",
    y = "Official Data: Yoshida Visitors"
  ) +
  theme_minimal()  # 简洁的主题
```
 
 
 
 - The results indicate that the Spearman correlation coefficient is 0.552, suggesting a moderate positive correlation between the two variables. Although this relationship is not very strong, it is still statistically significant.

## 5 Summaries

 - Peak hour at trailhead in 2024 became later in the day, median at around 14 pm
 - Peak hour at mountain in 2024 became later in the day, median around 14 pm
 - Peak hour at Half in 2024 became earlier in the day, median at around 9:00 am
 - Moderate positive correlation between KDDI data and MOE